### 2025-01-27 scripts/Paper-analysis.Rmd
use latest choice of sliding windo / step size

k=6 
```{r}
# Theoretical expectation for 6-bp palindrome density
theoreticalPalindromeExpectation = function(p){# p is GC content
  return ((p**2 - p + 1/2)**3)
}
d = read.csv('../test_output_window1000_step1000.csv', header=F, stringsAsFactors = F)
colnames(d) = c("PTU", "plasmid", "x", "window_size", "palindrome_count", "palindrome_density", "GC_n")

@@

# Maximum counts
d.reduced.median.plot = d.reduced.median %>% 
  group_by(PTU) %>%
  mutate(max_n = max(n, na.rm = TRUE),  # Calculate max 'n' for each 'PTU'
         normalized_n = n / max_n * 100) %>%  # Normalize 'n' by this max value
  ungroup() %>%  # Remove the grouping
  select(-max_n)  # Optionally remove the max_n column if not needed
# Plot the distribution
p.lines.expectation = ggplot(d.reduced.median.plot, aes(x, median))+
  geom_hline(yintercept = 0, linetype='dashed')+
  theme_bw()+
  geom_path(aes(group=PTU, alpha=normalized_n))+
  facet_wrap(~PTU, scales="free_x", nrow=3)+
  ylab("Deviation from expected 6-mer palindrome density (5kb sliding window)")+
  labs(alpha="% of plasmids within PTU")+
  theme(panel.grid=element_blank())+  
  scale_x_continuous(labels = function(x) x / 1000) +
  xlab("Position on plasmid (kb)")+
  theme(legend.position = c(0.8, 0.2))
ggsave(p.lines.expectation, file='../results/6mer-deviation-expectation.pdf',
       width=10, height=8)
```

>>>>

k=6 
```{r}
# Theoretical expectation for 6-bp palindrome density
theoreticalPalindromeExpectation = function(p){# p is GC content
  return ((p**2 - p + 1/2)**3)
}
d = read.csv('../test_output_window5000_step500.csv', header=F, stringsAsFactors = F)
colnames(d) = c("PTU", "plasmid", "x", "window_size", "palindrome_count", "palindrome_density", "GC_n")

@@

# Maximum counts
d.reduced.median.plot = d.reduced.median %>% 
  group_by(PTU) %>%
  mutate(max_n = max(n, na.rm = TRUE),  # Calculate max 'n' for each 'PTU'
         normalized_n = n / max_n * 100) %>%  # Normalize 'n' by this max value
  ungroup() %>%  # Remove the grouping
  select(-max_n)  # Optionally remove the max_n column if not needed
# Plot the distribution
p.lines.expectation = ggplot(d.reduced.median.plot, aes(x, median))+
  geom_hline(yintercept = 0, linetype='dashed')+
  theme_bw()+
  geom_path(aes(group=PTU, alpha=normalized_n))+
  facet_wrap(~PTU, scales="free_x", nrow=3)+
  ylab("Deviation from expected 6-mer palindrome density (5kb sliding window)")+
  labs(alpha="% of plasmids within PTU")+
  theme(panel.grid=element_blank())+  
  scale_x_continuous(labels = function(x) x / 1000) +
  xlab("Position on plasmid (kb)")+
  theme(legend.position = c(0.8, 0.2))
ggsave(p.lines.expectation, file='../results/6mer-deviation-expectation.pdf',
       width=10, height=6)
```
